Peering Through Censorship:\\Tackling Internet Censorship Using P2P Networking

### 2023-05-22 paper.tex
werk

Censorship circumvention has developped over several decades. Originating out of anonymity research, censorship resistance is a less difficult problem than full anonymity,\footnote{Anonymity generally requires censorship resistance (or a non-censoring adversary) to bootstrap.} and has become a topic studied on it's own independent of anonymity.\footnote{Though anonymity and censorship are distinct problems and are often approached independently in research, there is notable interaction between the two fields - many censorship circumvention techniques target the pluggable transport (PT) spec for deployment of censorship systems. The original PT spec was made for Tor, an anonymity network and protocol,\cite{tor} though later iterations of the spec are more general and are in use by tools including Tor, Lantern, and Psiphon.\cite{pt} In practice, current functional real world techniques all use the PT spec - see \ref{obfs} and \ref{snowflake} for details.} Censorship circumvention generally looks at one of two problems: proxying traffic \emph{out} of an adversaries sphere of influence, and providing access to those proxies to those within an adversaries sphere of influence.

@@

Beyond mimicry, most systems fall into either looking like an unkown protocol, or using an existing protocol as intended. We can also break down proxying techniques into low-bandwidth and high-bandwidth techniques. High-bandwidth, on it's own, is generally preferred to lower bandwidth, however, in censorship circumvention other tradeoffs exist - most notably, the cost of censoring many low-bandwidth channels is higher than many high bandwidth channels. These channels frequently use an existing protocol/service as intended, which means that censoring these channels may require taking down a high value service, e.g. if a circumvention system uses email effectively, it may only be possible to block by blocking email. We discuss several examples of both low and high bandwidth channels in the following sections. [TODO: Discuss the notion of signalling]

@@

@@

@@

Several high-bandwidth channels have been created, and at least two are in active use in real world situations. We first discuss channels that attempt to look like an unknown protocol, and then discuss ones that attempt to use existing protocols and services as intended.

@@

Scramblesuit had notable overhead from it's andshake phases. The UniformDH used modlar exponentiation, which is an expensive operation.\cite{obfs4} Additionally, Scramblesuit was vulnerable to some MitM attacks if the attacker knew the shared secret.\cite{obfs4} obfs4 replaced the UniformDH with use of Tor's ntor handshake, with obfuscation done by Elligator 2.\cite{obfs4} obfs4 is still in use today, and is one of the main two circumvention techniques used for circumventing censorship in the Tor browser.

[TODO: Wang et al, new censorship]

@@

\subsection{[P2P and P2P-like]}

\subsubsection{Snowflake}

@@

@@

\subsection{Decoy routing}

\subsubsection{Tapdance}

@@

>>>>

Censorship circumvention has developped over several decades. Originating out of anonymity research, censorship resistance is a less difficult problem than full anonymity,\footnote{Anonymity generally requires censorship resistance (or a non-censoring adversary) to bootstrap.} and has become a topic studied on it's own independent of anonymity.\footnote{Though anonymity and censorship are distinct problems and are often approached independently in research, there is notable interaction between the two fields - many censorship circumvention techniques target the pluggable transport (PT) spec for deployment of censorship systems. The original PT spec was made for Tor, an anonymity network and protocol,\cite{tor} though later iterations of the spec are more general and are in use by tools including Tor, Lantern, and Psiphon.\label{pt}\cite{pt} In practice, current functional real world techniques all use the PT spec - see \ref{obfs} and \ref{snowflake} for details.} Censorship circumvention generally looks at one of two problems: proxying traffic \emph{out} of an adversaries sphere of influence, and providing access to those proxies to those within an adversaries sphere of influence.

@@

Beyond mimicry, most systems fall into either looking like an unkown protocol, or using an existing protocol as intended. We can also break down proxying techniques into low-bandwidth and high-bandwidth techniques. High-bandwidth, on it's own, is generally preferred to lower bandwidth, however, in censorship circumvention other tradeoffs exist - most notably, the cost of censoring many low-bandwidth channels is higher than many high bandwidth channels. These channels frequently use an existing protocol/service as intended, which means that censoring these channels may require taking down a high value service, e.g. if a circumvention system uses email effectively, it may only be possible to block by blocking email. We discuss several examples of both low and high bandwidth channels in the following sections.

Lower and higher bandwidth transports can be combined to work together and gain benefits of both. Most higher-bandwidth channels require conveying some less-fixed \emph{out-of-band} information (e.g. an IP address) to use a higher bandwidth channel. Low bandwidth channels, generally being more costly to block, still require out-of-band information, but frequently this information is valid as long as the channel is functional. For example, an email-based channel will require a recipient email address, but this email address could be effectively constant due to the way email itself functions. As a result, an email based channel may effectively hard-code this information in the transport itself, allowing the channel to be used as long as you have the code and an adversary that does not block email. This highly resiliant but low-bandwidth setup may be used to bootstrap higher bandwidth channels. An email channel may be used to convey an IP address of a point to point high bandwidth channel, and could be used for important messages or to get another channel if the recieved point-to-point channel is blocked. With this synergy between the low and high bandwidth channels, discussing and understanding both is crucial to a modern circumvention system.

@@

[TODO: Discuss IP blocking]

@@

[TODO: Discuss false positives and base-rate fallacy]

@@

Several high-bandwidth channels have been created, and at least two are in active use in real world situations. We first discuss channels that attempt to look like an unknown protocol (UP), and then discuss ones that properly use protocols (PUP).

@@

Scramblesuit had notable overhead from it's handshake phases. The UniformDH used modular exponentiation, which is an expensive operation.\cite{obfs4} Additionally, Scramblesuit was vulnerable to some MitM attacks if the attacker knew the shared secret.\cite{obfs4} obfs4 replaced the UniformDH with use of Tor's ntor handshake, with obfuscation done by Elligator 2.\cite{obfs4} obfs4 is still in use today, and is one of the main two circumvention techniques used for circumventing censorship in the Tor browser. [TODO: cite] obfs4 requires some out of band info to function - which is done through hard-coding, email, telegram, or domain fronting. [TODO: xref]

Even though obfs4 is still functional and in use, that does not mean it is not vulnerable to attack. Wang et al demonstrated that obfs4 is vulnerable to entropy based attacks: conventional and often used web protocols, even if encrypted, usually have some control messages unencrypted - e.g. TLS and SSH both have unencrypted portions of the header. This means that the entropy of these flows is lower than that of obfs4 flows - because obfs4 attempts to look-like-nothing, it ends up looking like a fully encrypted stream with no plaintext, resulting in very high entropy - but, no well known protocol does this. By attempting to look like a hypothetical unknown protocol, obfs4 may actually look unique.\cite{wang} Obfs4 can be reliably detected and blocked as a result, with relatively low computational costs. There are some drawbacks to this - most notably the base-rate fallacy, discussed in Section \ref{base-rate}. This paper was published in 2015, though for over 5 years this attack was not observed by any adversaries. In 2021, these attacks were observed on the live internet, discussed further in Section \ref{entropy}.

Obfs4 also faces another problem: the bridge distribution problem, discussed further in Section \ref{bridge}. Bridges, once known by an adversary, can be blocked at the IP level, and the software is difficult for basic users to spin up. Some of these issues are addressed by Snowflake in Section \ref{snowflake}.

@@

\subsection{Properly using protocols}

Several transports attempt to use protocols as intended. Snowflake is in real world usage, and several others have been developed in the literature.

\subsubsection{Snowflake}
\label{snowflake}

Snowflake is a transport designed for usage by the Tor browser,\footnote{Though, it conforms to the PT spec spec, and as such could be used by other systems. See Section \ref{PT} for more on PTs.} and is currently in use in the real world. Snowflake seeks to offer an alternative way of spinning up proxies compare to obfs and other transports that rely on proxies with fixed IP addresses, as well as using a different transport. Snowflake does this by taking advantage of how modern browsers are setup to ease proxy deployment and transport development. These concepts were introduced by Flashproxy and other related work. Flashproxy defined three key problems that this class of transport must address: how to create proxies, how to rendezvous, and how to actually hide when in use.\cite{flashproxy} Flashproxy addresses proxy creation by allowing volunteers to embed code in their sites that turn any visitor into a proxy for censored users. These proxies are ephemeral, and are regular web users, changing up the cost and benefits a censor reaps if they were to be blocked. Rendezvous is handled by setting up a well-known connection broker. Hiding in use is not explored deeply, but is justified by simply using a frequently used web browser transport (WebSockets).

@@

\subsubsection{Decoy routing}

[Tapdance]

@@

@@

[https://gfw.report/publications/usenixsecurity23/data/paper/paper.pdf]
